Alexis Roche

### 2020-09-28 cv/cv.tex
Some CV modifs

\noindent Senior-level engineer and applied researcher with a specialist expertise in computer vision, medical image analysis and machine learning, operating in the fields of applied research, healthcare, electro-domestic and entertainment industry. Graduated from the French ``Grande \'Ecole" CentraleSupelec (formely, Centrale Paris), and holder of a PhD. Strong experience in developing research and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, machine learning, deep learning, statistics, brain imaging, Python, C.

@@

\ \\
\noindent \textbf{NEUROIMAGING:} Extensive experience in developing algorithms for structural and functional brain magnetic resonance imaging (MRI) in the form of open-source and commercial software for neuroscience, clinical research \& clinical practice.

@@

\ \\
\noindent \textbf{INTERACTION:} Proven ability to work in multidisciplinary environments at the interface of industry and academic research, as well as to develop successful collaborations with physicians and fundamental life science researchers.

\ \\
\noindent \textbf{SCIENTIFIC WRITING:} Main author of 25 peer-reviewed scientific articles published in international journals, proceedings and books, co-author of more than 100 scholarly publications and 5 international patents.

@@

\bighead{SENIOR COMPUTER VISION ENGINEER}{Didimo, Porto, Portugal}{2019--present}
\nopagebreak
\begin{itemize}
\item Developing computer vision algorithms for high-fidelity 3D avatars.
\end{itemize}
\ \\

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} C/C++ \\
{\tiny$\bullet$} Python (numpy, scipy, pylab, skimage, opencv, sklearn, TensorFlow, keras, cython...)\\ 
{\tiny$\bullet$} Matlab\\
{\tiny$\bullet$} R. \\
{\tiny$\bullet$} Version control software (git, svn).\\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6102 citations, h-index: 34, i10-index: 62 (April 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}

>>>>

\noindent Scientific team leader with a specialist expertise in computer vision, data science and machine learning, who has operated in the fields of academic research, healthcare, electro-domestic and entertainment industry. Graduated from \'Ecole Centrale Paris, and holder of a PhD in Engineering Science. Strong experience in the development of both open source and commercial software. {\em Keywords:} artificial intelligence, image processing, computer vision, medical image analysis, machine learning, deep learning, statistics, Python,~C.

@@

@@

\ \\
\noindent \textbf{SCIENTIFIC WRITING:} Main author of 25 peer-reviewed scientific articles published in international journals, proceedings and books, co-author of more than 100 scholarly publications and 5 published international patents.

\ \\
\noindent \textbf{TECHNICAL LEADERSHIP:} Proven ability to coordinate a team and manage objectives in multidisciplinary environments.

%\ \\
%\noindent \textbf{NEUROIMAGING:} Extensive experience in developing algorithms for structural and functional brain magnetic resonance imaging (MRI) in the form of open-source and commercial software for neuroscience, clinical research \& clinical practice.

@@

\bighead{COMPUTER VISION \& ARTIFICIAL INTELLIGENCE TEAM LEADER}{Didimo, Porto, Portugal}{2019--present}
\nopagebreak
\begin{itemize}
\item Developing computer vision and machine learning algorithms for high-fidelity 3D avatars.
\end{itemize}
\ \\

@@

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Programming:}
\ \\ 
\ \\
\ \\ 
\ \\
\ \\ 
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} C/C++ \\
{\tiny$\bullet$} Python (numpy, scipy, pylab, skimage, opencv, sklearn, TensorFlow, Keras, ...)\\
{\tiny$\bullet$} C/Python integration via Cython\\
{\tiny$\bullet$} Matlab\\
{\tiny$\bullet$} R \\
{\tiny$\bullet$} Version control software: Git, SVN, Perforce. \\
\end{minipage}

\ \\
\noindent 
\begin{minipage}{.15\textwidth}
\textbf{Publications:}
\ \\ 
\ \\
\ \\
\ \\
\end{minipage}
\begin{minipage}{.85\textwidth}
{\tiny$\bullet$} 115 scholarly publications.\\
{\tiny$\bullet$} Full list available at ORCID: \url{http://orcid.org/0000-0002-4821-6893} \\
{\tiny$\bullet$} Google scholar statistics: 6396 citations, h-index: 35, i10-index: 64 (September 2020).\\
{\tiny$\bullet$} 5 published international patents. \\
\end{minipage}
